---
title: "County Averages"
author: "Rob Wells"
date: "3/22/2021"
output: html_document
---
# Part 1: Import State Data, Clean It

```{r include=FALSE}
#install.packages("slider")
#install.packages("zoo")
#install.packages("gtools")
#install.packages("formattable")
library(tidyverse)
library(janitor)
library(lubridate)
library(tidyr)
library(jsonlite)
library(gtools)
library(zoo)  
library(reshape2)
library(slider)
library(formattable)
```

## Retrieve State Arkansas Covid Data from ADH FEED
```{r}
#New County json feed
#38 Variables
q <- fromJSON('https://services.arcgis.com/PwY9ZuZRDiI5nXUB/ArcGIS/rest/services/UPDATED_ADH_COVID19_COUNTY_METRICS/FeatureServer/0/query?where=0%3D0&objectIds=&time=&geometry=&geometryType=esriGeometryEnvelope&inSR=&spatialRel=esriSpatialRelIntersects&resultType=none&distance=0.0&units=esriSRUnit_Meter&returnGeodetic=false&outFields=*&returnGeometry=true&returnCentroid=false&featureEncoding=esriDefault&multipatchOption=xyFootprint&maxAllowableOffset=&geometryPrecision=&outSR=&datumTransformation=&applyVCSProjection=false&returnIdsOnly=false&returnUniqueIdsOnly=false&returnCountOnly=false&returnExtentOnly=false&returnQueryGeometry=false&returnDistinctValues=false&cacheHint=false&orderByFields=&groupByFieldsForStatistics=&outStatistics=&having=&resultOffset=&resultRecordCount=&returnZ=false&returnM=false&returnExceededLimitFeatures=true&quantizationParameters=&sqlFormat=none&f=pjson&token=')

df3 <- q[["features"]][["attributes"]]
#print's today's date as a date field
df3$mydate <- Sys.Date()
#file.exists(filename)
#austin help on that
#if file exists = check if current data is different and if that is true then append today's data set to master dataset and resave
today_county <- df3
```

```{r}
#If this fails, check the backup from Austin
#https://docs.google.com/spreadsheets/d/1WRITgZZdI5PwiJiJeutBjJigSifOaNPDyTW_jHizfGQ/edit?usp=sharing
```



```{r}
today_county <- janitor::clean_names(today_county)
```


#Set Dates
```{r}
#today's date
today <- Sys.Date()

#NOTE: IF YOU ARE RUNNING THIS A DAY LATE, USE THIS CODE TO WORK PROPERLY
#today <- Sys.Date()-1
#today_county$mydate <-"2020-09-22- THE OLD DATE...."

#yesterday's date
yesterday <- (today-1)

```

#Quick Calculation of State Totals 
```{r}
today_county <- today_county [ -c(1) ]
today_county [2:37] <- lapply(today_county [2:37], as.numeric)
#Calculate statewide totals

today_county <- today_county %>%
  janitor::adorn_totals("row") %>% 
  mutate(mydate=(today))

today_county$county_nam <- str_replace_all(today_county$county_nam, pattern=fixed('Arkansas'), replacement=fixed('Arkansas_county') )
today_county$county_nam <- str_replace_all(today_county$county_nam, pattern=fixed('Total'), replacement=fixed('Arkansas_all_counties') )
today_county$county_nam  <- gsub("[[:space:]]", "", today_county$county_nam)
today_county$mydate <- as.Date(today_county$mydate)
```

-**Import and Clean Yesterday's Data**
```{r}
yesterday_county <- rio::import("https://raw.githubusercontent.com/Arkansascovid/Main/master/master_file.csv")
#yesterday_county <- yesterday_county [ -c(1) ]
yesterday_county$mydate <- as.Date(yesterday_county$mydate)
#ran this to test it out on today's data
 yesterday_county <- yesterday_county %>% 
  filter(mydate<=(yesterday))
yesterday_county[4:45] <- lapply(yesterday_county[4:45], as.numeric)
```
# .
# Previous Date Calculations
#  .
-**This section performs all of the county calculations**   
-**It updates master_file.csv**  
-**Create Temporary Table Two Days' Worth of Data**   
-**Sort Alphbetically and Run Calculations**   

```{r}
countytemp <- yesterday_county %>% 
  filter(mydate>=(yesterday)) %>%  
  arrange(county_nam) 
```

You should get a df with 154 observations (two days' worth a data)
```{r}
df_master <- smartbind(today_county, countytemp)

twodays <- df_master %>% 
  arrange((county_nam))
```


-**The Today-Yesterday Calculations**

```{r}
twodays <- twodays %>%
  mutate(Number_Tested=(positive+negative)) %>% 
  mutate(New_Cases_Today = (positive-lead(positive))) %>%
  mutate(Recovered_Since_Yesterday = (recoveries-lead(recoveries))) %>%
  mutate(New_Deaths_Today = (deaths-lead(deaths))) %>%
  mutate(New_Tests_Dashboard = (Number_Tested-lead(Number_Tested)))
```

- **IMPORTANT: FILTER TABLE TO TODAY'S RESULTS**
```{r}
twodays <- twodays %>% filter(mydate > yesterday) #SHOULD GET 77 ROWS IN twodays
```


```{r}
glimpse(twodays)
```

-**The Percentage Calculations**

```{r}
twodays <- twodays %>%
  mutate(Cases_Population = (positive / pop_5yr_est_2018)*100) %>% 
  mutate(Tested_Population = (Number_Tested / pop_5yr_est_2018)*100) %>% 
  mutate(New_Cases_Today_10k_Pop = (New_Cases_Today/pop_5yr_est_2018)*10000) %>% 
  mutate(Active_Cases_10k_Pop = (confirmed_active/pop_5yr_est_2018)*10000) %>% 
  mutate(Pct_Positive_Cumulative = (positive/Number_Tested)*100) %>% 
  mutate(Pct_Positive_New_to_Dashboard = (New_Cases_Today/New_Tests_Dashboard)*100) %>% 
  mutate(Closed = (recoveries + deaths)) %>% 
  mutate(Pct_Deaths_vs_Recoveries = (deaths/Closed)*100) %>% 
  mutate(Pct_Recoveries_vs_Deaths = (recoveries/Closed)*100)
  
twodays
```

#Merges the Today's Arkanas_All_Counties line with yesterday's data. 
```{r}
master2 <- smartbind(twodays, yesterday_county, fill=0)
```

```{r}

master2 <- master2 %>% 
  select("county_nam","mydate","deaths","fhwa_numbe","fips","positive","negative","recoveries","total_tests","active_cases","pop_5yr_est_2018","confirmed_pos","probable_pos","confirmed_neg","probable_neg","confirmed_recov","probable_recov","confirmed_death","probable_death", "confirmed_active","probable_active","pcr_test","antigen_test","pcr_pos_test", "pcr_neg_test","antigen_pos_test","antigen_neg_test","total_pos_test","total_neg_test",
"New_Cases_Today","Recovered_Since_Yesterday","New_Deaths_Today","New_Tests_Dashboard","Cases_Population","Tested_Population","New_Cases_Today_10k_Pop","Active_Cases_10k_Pop","Pct_Positive_Cumulative","Pct_Positive_New_to_Dashboard","Closed","Pct_Deaths_vs_Recoveries","Pct_Recoveries_vs_Deaths","lab_prvt","lab_pub")
master2$mydate <- as.Date(master2$mydate)
glimpse(master2)
```


#Save master file
```{r}
master2$Cases_Population <- round(master2$Cases_Population, 2)
master2$Tested_Population <- round(master2$Tested_Population, 2)
master2$New_Cases_Today_10k_Pop <- round(master2$New_Cases_Today_10k_Pop, 2)
master2$Active_Cases_10k_Pop <- round(master2$Active_Cases_10k_Pop, 2)
master2$Pct_Positive_Cumulative <- round(master2$Pct_Positive_Cumulative, 2)
master2$Pct_Positive_New_to_Dashboard <- round(master2$Pct_Positive_New_to_Dashboard, 2)
master2$Pct_Deaths_vs_Recoveries <- round(master2$Pct_Deaths_vs_Recoveries, 2)
master2$Pct_Recoveries_vs_Deaths <- round(master2$Pct_Recoveries_vs_Deaths, 2)

#write.csv(master2, "master_file_9_18.csv")
#write.csv(master2, file = "MasterData/master_file.csv")
```
# AVERAGE CALCULATIONS 
```{r}
test <- master2 %>% 
  group_by(county_nam) %>%
  arrange(county_nam, mydate) %>%
  mutate(Positive_7_Day_Avg = slider::slide_dbl(positive, mean, .before = 6, .after = 0)) %>%
  mutate(New_Cases_7_Day_Avg = slider::slide_dbl(New_Cases_Today, mean, .before = 6, .after = 0)) %>%
  mutate(New_Deaths_7_Day_Avg = slider::slide_dbl(New_Deaths_Today, mean, .before = 6, .after = 0)) %>%
    mutate(Active_Cases_7_Day_Avg = slider::slide_dbl(active_cases, mean, .before = 6, .after = 0)) %>%
ungroup()

#Run this before writing script to get back in descending order by date

test <- test %>% 
  arrange(desc(mydate))

county_averages <- test %>% 
  select(mydate, county_nam, positive, Positive_7_Day_Avg, New_Cases_Today, New_Cases_7_Day_Avg, New_Deaths_Today, New_Deaths_7_Day_Avg, Recovered_Since_Yesterday, active_cases, Active_Cases_7_Day_Avg) 

#Alex Nichol decimal rounding:
county_averages$Positive_7_Day_Avg <-round(county_averages$Positive_7_Day_Avg, 2)
county_averages$New_Cases_7_Day_Avg <-round(county_averages$New_Cases_7_Day_Avg, 2)
county_averages$New_Deaths_7_Day_Avg <-round(county_averages$New_Deaths_7_Day_Avg, 2)
county_averages$Active_Cases_7_Day_Avg <-round(county_averages$Active_Cases_7_Day_Avg, 2)

write.csv(county_averages, "county_averages.csv")
```

```{r}
county_latest <- subset(county_averages, mydate > "2021-03-14" & mydate < "2021-03-22")

write.csv(county_latest, "county_latest.csv")
```

