---
title: "Occupational Data"
author: "Mary Hennigan and Rob Wells and Abby Zimmardi" 
date: "2/10/2021"
output: pdf_document
---

# Compilation of Occupational COVID-19 Reports for Calculations

- **This notebook retrieves data from a Google sheet and compiles a time series of ADH occupational infection reports**

--**This 1/26 version created a time series from May 17 - Aug 20**

-**It will create a masterfile: occupation_master.csv**

# Part 1: Import Data, Clean It

```{r include=FALSE}
#install.packages("slider")
#install.packages("zoo")
#install.packages("gtools")
# vignette("basic-usage", package="googlesheets")
#install.packages("googledrive")
#install.packages("googlesheets4")
library(tidyverse)
library(janitor)
library(lubridate)
library(googlesheets4)
library(googledrive)
library(tidyr)
library(jsonlite)
library(gtools)
library(zoo)
library(reshape2)
library(slider)
```

#We have two spreadsheets in Google. One has the data from May 25-August 20


Import data from Hard Drive 
```{r}
 # occupation5_25 <- rio::import("/Users/maryhennigan/Downloads/OSHA Project 2021/OccupationMaster.xlsx", which = "525 Occupational")
```

#Wells 
```{r}
  occupation5_25 <- rio::import("/Users/rswells/Dropbox/Classes/Data Spring 2021/Facilities-Occupational Cases-Deaths.xlsx", which = "525 Occupational")


```


#This section for building the table from individual sheets
```{r include=FALSE}
 occupation5_25 <- rio::import("Facilities-Occupational Cases-Deaths.xlsx", which = "525 Occupational")
 occupation5_29 <- rio::import("Facilities-Occupational Cases-Deaths.xlsx", which = "529 Occupational")
 occupation6_2 <- rio::import("Facilities-Occupational Cases-Deaths.xlsx", which = "62 Occupational")
 occupation5_25$date <- "2020-5-25"
 occupation5_29$date <- "2020-5-29"
 occupation6_2$date <- "2020-6-2"
 occupation6_5 <- rio::import("Facilities-Occupational Cases-Deaths.xlsx", which = "65 Occupational")
 occupation6_9 <- rio::import("Facilities-Occupational Cases-Deaths.xlsx", which = "69 Occupational")
 occupation6_12 <- rio::import("Facilities-Occupational Cases-Deaths.xlsx", which = "612 Occupational")
 occupation6_14 <- rio::import("Facilities-Occupational Cases-Deaths.xlsx", which = "614 Occupational")
 occupation6_18 <- rio::import("Facilities-Occupational Cases-Deaths.xlsx", which = "618 Occupational")
 occupation6_5$date <- "2020-6-05"
 occupation6_9$date <- "2020-6-09"
 occupation6_12$date <- "2020-6-12"
 occupation6_14$date <- "2020-6-14"
 occupation6_18$date <- "2020-6-18"
 occupation6_25 <- rio::import("Facilities-Occupational Cases-Deaths.xlsx", which = "625 Occupational")
 occupation6_28 <- rio::import("Facilities-Occupational Cases-Deaths.xlsx", which = "628 Occupational")
 occupation7_3 <- rio::import("Facilities-Occupational Cases-Deaths.xlsx", which = "73 Occupational")
 occupation7_6 <- rio::import("Facilities-Occupational Cases-Deaths.xlsx", which = "76 Occupational")
 occupation6_25$date <- "2020-6-25"
 occupation6_28$date <- "2020-6-28"
 occupation7_3$date <- "2020-7-03"
 occupation7_6$date <- "2020-7-06"
 occupation7_14 <- rio::import("Facilities-Occupational Cases-Deaths.xlsx", which = "714 Occupational")
 occupation7_21 <- rio::import("Facilities-Occupational Cases-Deaths.xlsx", which = "721 Occupational")
 occupation7_24 <- rio::import("Facilities-Occupational Cases-Deaths.xlsx", which = "724 Occupational")
 occupation8_3 <- rio::import("Facilities-Occupational Cases-Deaths.xlsx", which = "83 Occupational")
 occupation8_7 <- rio::import("Facilities-Occupational Cases-Deaths.xlsx", which = "87 Occupational")
 occupation7_14$date <- "2020-7-14"
 occupation7_21$date <- "2020-7-21"
 occupation7_24$date <- "2020-7-24"
 occupation8_3$date <- "2020-8-03"
 occupation8_7$date <- "2020-8-07"
 occupation8_10 <- rio::import("Facilities-Occupational Cases-Deaths.xlsx", which = "810 Occupational")
 occupation8_20 <- rio::import("Facilities-Occupational Cases-Deaths.xlsx", which = "820 Occupational")
 occupation8_10$date <- "2020-8-10"
 occupation8_20$date <- "2020-8-20"
```


```{r}
glimpse(occupation5_25)
```

```{r warning=FALSE}
#Changed name to occupation_may_august
occupation_may_august <- smartbind(occupation5_25, occupation5_29, occupation6_2, occupation6_12, occupation6_25, occupation6_28, occupation6_9, occupation7_14, occupation7_21, occupation7_24, occupation7_3, occupation7_6, occupation8_10, occupation8_20, occupation8_3, occupation8_7)

#This combines occupational data from May 25 through Aug 20
write.csv(occupation_may_august, "occupationalmay_august.csv")

```

#The second spreadsheet has the data from September to February 2021
# https://docs.google.com/spreadsheets/d/1R5dVT4QN586ANvAH1SJ7ye94Br5OtrZsAA2e4KlWn0o/edit#gid=100802501


##import the file from your hard drive

```{r}
# occupation10_1 <- rio::import("/Users/maryhennigan/Downloads/OSHA Project 2021/Occupationals from PDFs.xlsx", which = "Occupational 10-1")

```

##pull in the sheets
#This section for building the table from individual sheets
```{r include=FALSE}
 occupation10_1 <- rio::import("Occupationals from PDFs.xlsx", which = "Occupational 10.1")
occupation10_5 <- rio::import("Occupationals from PDFs.xlsx", which = "Occupational 10.5")
occupation10_8 <- rio::import("Occupationals from PDFs.xlsx", which = "Occupational 10.8")
occupation10_12 <- rio::import("Occupationals from PDFs.xlsx", which = "Occupational 10.12")
occupation10_15 <- rio::import("Occupationals from PDFs.xlsx", which = "Occupational 10.15")
occupation10_19 <- rio::import("Occupationals from PDFs.xlsx", which = "Occupational 10.19")
occupation10_22 <- rio::import("Occupationals from PDFs.xlsx", which = "Occupational 10.22")
occupation10_26 <- rio::import("Occupationals from PDFs.xlsx", which = "Occupational 10.26")
occupation10_29 <- rio::import("Occupationals from PDFs.xlsx", which = "Occupational 10.29")
occupation9_3 <- rio::import("Occupationals from PDFs.xlsx", which = "Occupational 9.3")
occupation9_7 <- rio::import("Occupationals from PDFs.xlsx", which = "Occupational 9.7")
occupation9_9 <- rio::import("Occupationals from PDFs.xlsx", which = "Occupational 9.9")
occupation9_14 <- rio::import("Occupationals from PDFs.xlsx", which = "Occupational 9.14")
occupation9_28 <- rio::import("Occupationals from PDFs.xlsx", which = "Occupational 9.28")
occupation8_17 <- rio::import("Occupationals from PDFs.xlsx", which = "Occupational 8.17")
occupation8_24 <- rio::import("Occupationals from PDFs.xlsx", which = "Occupational 8.24")
occupation8_27 <- rio::import("Occupationals from PDFs.xlsx", which = "Occupational 8.27")
occupation8_31 <- rio::import("Occupationals from PDFs.xlsx", which = "Occupational 8.31")
occupation11_2 <- rio::import("Occupationals from PDFs.xlsx", which = "Occupational 11.02")
occupation11_5 <- rio::import("Occupationals from PDFs.xlsx", which = "Occupational 11.05")
occupation11_9 <- rio::import("Occupationals from PDFs.xlsx", which = "Occupational 11.09")
occupation11_12 <- rio::import("Occupationals from PDFs.xlsx", which = "Occupational 11.12")
occupation11_16 <- rio::import("Occupationals from PDFs.xlsx", which = "Occupational 11.16")
occupation11_19 <- rio::import("Occupationals from PDFs.xlsx", which = "Occupational 11.19")
occupation11_23 <- rio::import("Occupationals from PDFs.xlsx", which = "Occupational 11.23")
occupation11_26 <- rio::import("Occupationals from PDFs.xlsx", which = "Occupational 11.26")
occupation11_30 <- rio::import("Occupationals from PDFs.xlsx", which = "Occupational 11.30")
occupation12_3 <- rio::import("Occupationals from PDFs.xlsx", which = "Occupational 12.3")
occupation12_7 <- rio::import("Occupationals from PDFs.xlsx", which = "Occupational 12.7")
occupation12_14 <- rio::import("Occupationals from PDFs.xlsx", which = "Occupational 12.14")
occupation12_17 <- rio::import("Occupationals from PDFs.xlsx", which = "Occupational 12.17")
occupation12_21 <- rio::import("Occupationals from PDFs.xlsx", which = "Occupational 12.21")
occupation12_24 <- rio::import("Occupationals from PDFs.xlsx", which = "Occupational 12.24")
occupation12_28 <- rio::import("Occupationals from PDFs.xlsx", which = "Occupational 12.28")
occupation12_31 <- rio::import("Occupationals from PDFs.xlsx", which = "Occupational 12.31")
occupation1_4 <- rio::import("Occupationals from PDFs.xlsx", which = "Occupational 1.04")
occupation1_7 <- rio::import("Occupationals from PDFs.xlsx", which = "Occupational 1.07")
occupation1_11 <- rio::import("Occupationals from PDFs.xlsx", which = "Occupational 1.11")
occupation1_14 <- rio::import("Occupationals from PDFs.xlsx", which = "Occupational 1.14")
occupation1_18 <- rio::import("Occupationals from PDFs.xlsx", which = "Occupational 1.18")
occupation1_21 <- rio::import("Occupationals from PDFs.xlsx", which = "Occupational 1.21")
occupation1_25 <- rio::import("Occupationals from PDFs.xlsx", which = "Occupational 1.25")
occupation1_28 <- rio::import("Occupationals from PDFs.xlsx", which = "Occupational 1.28")
#Add new dates here
occupation2_1 <- rio::import("Occupationals from PDFs.xlsx", which = "Occupational 2.01")

```

#Clean and Normalize Names
```{r include=FALSE}
occupation10_1 <- clean_names(occupation10_1)
occupation10_5 <- clean_names(occupation10_5)
occupation10_8 <- clean_names(occupation10_8)
occupation10_12 <- clean_names(occupation10_12)
occupation10_15 <- clean_names(occupation10_15)
occupation10_19 <- clean_names(occupation10_19)
occupation10_22 <- clean_names(occupation10_22)
occupation10_26 <- clean_names(occupation10_26)
occupation10_29 <- clean_names(occupation10_29)
occupation9_3 <- clean_names(occupation9_3)
occupation9_7 <- clean_names(occupation9_7)
occupation9_9 <- clean_names(occupation9_9)
occupation9_14 <- clean_names(occupation9_14)
occupation9_28 <- clean_names(occupation9_28)
occupation8_17 <- clean_names(occupation8_17)
occupation8_24 <- clean_names(occupation8_24)
occupation8_27 <- clean_names(occupation8_27)
occupation8_31 <- clean_names(occupation8_31)
occupation11_2 <- clean_names(occupation11_2)
occupation11_5 <- clean_names(occupation11_5)
occupation11_9 <- clean_names(occupation11_9)
occupation11_12 <- clean_names(occupation11_12)
occupation11_16 <- clean_names(occupation11_16)
occupation11_19 <- clean_names(occupation11_19)
occupation11_23 <- clean_names(occupation11_23)
occupation11_26 <- clean_names(occupation11_26)
occupation11_30 <- clean_names(occupation11_30)

occupation12_3 <- clean_names(occupation12_3)
occupation12_7 <- clean_names(occupation12_7)
occupation12_14 <- clean_names(occupation12_14)
occupation12_17 <- clean_names(occupation12_17)
occupation12_21 <- clean_names(occupation12_21)
occupation12_24 <- clean_names(occupation12_24)
occupation12_28 <- clean_names(occupation12_28)
occupation12_31 <- clean_names(occupation12_31)

occupation1_4 <- clean_names(occupation1_4)
occupation1_7 <- clean_names(occupation1_7)
occupation1_11 <- clean_names(occupation1_11)
occupation1_14 <- clean_names(occupation1_14)
occupation1_18 <- clean_names(occupation1_18)
occupation1_21 <- clean_names(occupation1_21)
occupation1_25 <- clean_names(occupation1_25)
occupation1_28 <- clean_names(occupation1_28)
occupation2_1 <- clean_names(occupation2_1)

```


#Combine through 9-14
#This creates an employer db from Aug 17-Sept 14
```{r warning=FALSE}

employer_master <- smartbind(occupation8_17, occupation8_24, occupation8_27, occupation8_31, occupation9_14, occupation9_3, occupation9_7, occupation9_9)
```


#This creates an industry db from Sept 28-Feb 1, 2021. It lacks the Employer Names
```{r warning=FALSE}
#This creates an industry db from Sept 28-Feb 1, 2021. It lacks the Employer Names
industry_master <- smartbind(occupation2_1, occupation1_28, occupation1_25, occupation1_11, occupation1_7, occupation1_4, occupation12_31, occupation12_28, occupation12_3, occupation12_24, occupation12_21, occupation12_17, occupation12_14, occupation11_9, occupation11_5, occupation11_30, occupation11_26, occupation11_23, occupation11_2, occupation11_19, occupation11_16, occupation11_12, occupation10_8, occupation10_5, occupation10_29, occupation10_22, occupation10_19, occupation10_26, occupation10_15, occupation10_12, occupation10_1, occupation12_7, occupation9_28, occupation1_21, occupation1_18, occupation1_14)

#occupation_master2 <- occupation_master2[ -c(3,4,5,6) ]

#arrange(occupation_master2,desc(Date))
employer_master$date <- ymd(employer_master$date)
industry_master$date <- ymd(industry_master$date)   

write.csv(employer_master,"employer_master.csv")

glimpse(industry_master)

```


#separate the company and city by comma
#from this script: https://profrobwells.github.io/HomelessSP2020/SF_311_Calls_UofA.html
#split data into two columns
#SF <- separate(data = SF, col = crime1, into = c("crime2", "crime3", "crime4"), sep = " ", extra = "merge", fill = "right")

```{r}
#311 records
industry_master <- separate(data = industry_master, col = industry_city_county, into = c("industry", "city", "county"), sep = ",", extra = "merge", fill = "right")

industry_master <- clean_names(industry_master)


industry_master$city <- str_trim(industry_master$city, side = c("both"))
industry_master$county <- str_trim(industry_master$county,  side = c("both"))
write.csv(industry_master,"industry_master.csv")
glimpse(industry_master)
```

#Import 329 records of company names and dates.
```{r}
#329 records
names <- rio::import("Facilities-Occupational Cases-Deaths.csv")
names$Date <- ymd(names$Date)
write.csv(names,"names.csv")
glimpse(names)
```
#Join the Industry and Names Files

#Howard Center People Start Here:
```{r}
#329 records from Sept 17 to Jan 28
names <- rio::import("https://raw.githubusercontent.com/profrobwells/Spring2021Data/main/names.csv")
#311 records from Sept 28 to Feb 1
industry_master <- rio::import("https://raw.githubusercontent.com/profrobwells/Spring2021Data/main/industry_master.csv")


#This is the first problem: ADH gave us more names than industry records. Check that Sept 17 doesn't have 18 record that would account for the difference.

```

#We now join the industry db with a list of company names and dates

```{r}
joined_industry_names <- industry_master %>% 
  inner_join(names, by=c("date"="Date", "city"="City", "county"="County"))

write.csv(joined_industry_names,"joined_indstry_names.csv")

#Now 375 records. 64 extra than the source industry file

#Problem: 369 records, 58 extra than the source industry file
#It is posting double entries on some dates
```

```{r}
#Analyze records by date and location
names %>% 
  select(Date, City, County) %>% 
  group_by(Date, City, County) %>% 
  count() %>% 
  arrange(desc(n))
  
```

```{r}
industry_master %>% 
  select(date, city, county) %>% 
  group_by(date, city, county) %>% 
  count() %>% 
  arrange(desc(n))
#join all of the one values
#filter to 1 and join that to original df (master)

#clean industry master to get rid of entertainment
#Test on 12-17-2020 Jonesboro. five cases dont match with the five companies.
```

#Possible Fix: Have them all the same date period: Sept 28-Jan 28
```{r}
#318 records
names2 <- names %>% 
  filter(Date >= "2020-09-28")

#307 records
industry_master2 <- industry_master %>% 
  filter(date >= ("2020-09-28")) %>% 
  filter(date <= ("2021-01-28"))
```
#What's messed up about this is the ADH gave us records for 11 more cases than what they reported.
#We should check to see if we have all the records by date for the names and industry master - see if there are some date or record gaps in industry master

#Anyway, we join again
```{r}
joined2 <- industry_master2 %>% 
  inner_join(names2, by=c("date"="Date", "city"="City", "county"="County"))


#Problem: Still 375 records, now 68 extra than the source industry file
#It is still posting double entries on some dates
```

#End of dilemma#

```{r}
industry_date <- industry_master %>% 
  count(date)

names_date <- names %>% 
  count(Date)
```

```{r}
nomatches <- industry_date %>% 
  anti_join(names_date, by=c("date"="Date", "n"="n"))
nomatches
#Oct 10, 5 records not in the Names file
#Nov 16 11 in names but 10 in industry
#Jan 18 14 in names but 15 in industry
#Feb 1 4 records not in Names file

```


#Notes Below#


#This section is aimed at running down the duplication

#73 records in the names file
```{r}
names_original <- names %>% 
  count(`Business Name`)
```

#68 records in the joined file
```{r}
joined_db <- joined %>% 
  count(`Business Name`)
```



```{r}
#problem: 403 records
joined2 <- industry_master %>% 
  left_join(names, by=c("date"="Date", "city"="City", "county"="County"))

```


###Format Dates
```{r}
library(lubridate)

names$year <- year(names$Date)
names$month <- month(names$Date, label=TRUE)
names$week <- week(names$Date)
names$day <- day(names$Date)
names$weekday <- wday(names$Date, label=TRUE, abbr=FALSE)


employer_master$year <- year(employer_master$date)
employer_master$month <- month(employer_master$date, label=TRUE)
employer_master$week <- week(employer_master$date)
employer_master$day <- day(employer_master$date)
employer_master$weekday <- wday(employer_master$date, label=TRUE, abbr=FALSE)



industry_master$year <- year(industry_master$date)
industry_master$month <- month(industry_master$date, label=TRUE)
industry_master$week <- week(industry_master$date)
industry_master$day <- day(industry_master$date)
industry_master$weekday <- wday(industry_master$date, label=TRUE, abbr=FALSE)
glimpse(industry_master)
```

```{r}
#Mini table
mini <- employer_master %>% 
  select(employer_city_county, date, year, month, week, day, weekday,total_number_of_cases)
mini
```




```{r}
sep <- employer_master %>% 
  select("employer_city_county", "date", "month", "total_number_of_cases") %>% 
filter(month == "Sep") %>% 
  arrange(desc("total_number_of_cases"))

sep


```


#fix this

```{r}
#Mini table
mini_industry <- industry_master %>% 
  select(industry_city_county, date, year, month, week, day, weekday,total_number_of_cases)
mini_industry
```

```{r}
oct <- industry_master %>% 
  select("industry_city_county", "date", "month", "total_number_of_cases") %>% 
filter(month == "Oct") %>% 
  arrange(desc("date"))

oct
write.csv(oct, "oct_industry.csv")

```




