---
title: "Occupational analysis exercises"
author: "Rob Wells"
date: "4/12/2021"
output: 
  html_document:
      toc: true
      toc_float: true
      toc_depth: 4
---
 
### Analysis of ADH occupational data


- **This tutorial uses a subset of this data** 

    The Calls for Service were filtered as follows: 
    CONTAINS homeless, 915, 919, 920: Downloaded 157,237 records 3/31/16 to 11/30/2019. 
    This is 5.1% of all calls in the broader database.
    File renamed to: SF_311_Jan29.xlsx   
   
# Part 1: Import Data, Clean It

```{r include=FALSE}
#install.packages("slider")
#install.packages("zoo")
#install.packages("gtools")
# vignette("basic-usage", package="googlesheets")
#install.packages("googledrive")
#install.packages("googlesheets4")
library(tidyverse)
library(janitor)
library(lubridate)
library(tidyr)
library(jsonlite)
library(gtools)
library(zoo)
library(reshape2)
library(slider)
library(rio)
library(dplyr)
```

Load Data
```{r}
adh_cleaned <- rio::import("https://raw.githubusercontent.com/profrobwells/Spring2021Data/main/cleaned_master.csv") 
```

```{r}
glimpse(adh_cleaned)
```


- **Count companies**
```{r}
company <- adh_cleaned %>% 
  count(company_name) %>% 
  arrange(desc(n))
company
```

- **Count cleaned_companies**
```{r}
company_cleaned <- adh_cleaned %>% 
  count(cleaned_company) %>% 
  arrange(desc(n))
company_cleaned
```

#YOUR TURN
#Count counties, then cleaned counties


#Time analysis

- **Cases by month**
```{r}
months <- adh_cleaned %>% 
  count(yearmon) %>% 
  group_by(yearmon) %>% 
  arrange(desc(yearmon))
months
```

```{r}
Days <- adh_cleaned %>% 
  count(date) %>% 
  group_by(date) %>% 
  arrange(desc(n))
Days
#July 3 was the day with the most reports. Some 25 separate entries on covid workplace cases
#Feb 21, 2021 had the fewest, with one report
```


#Summary: Using the summary() function, describe the minimum, maximum, median and mean of calls in the various columns with integers
#number_active_cases  
#number_recovered_cases 
#total_number_of_cases  
```{r}
summary(adh_cleaned$number_active_cases)
```

Between May 19, 2020 and Feb. 22, 2021, there were an **an average 13 active COVID-19 cases** per reporting period


#Example code to Export a table into a spreadsheet (csv is a comma separated file)
```{r}
write.csv(Days,"Days.csv")
```


#---------------------------------------------------------------------------------------------
#NOTES BELOW
#---------------------------------------------------------------------------------------------
#Revision: 10,985 cases total cases of infected employees in Arkansas workplaces. 
#Previous: 11,103 

```{r}
companytotals <- cleaned_master %>% 
  select(company_name, cleaned_company, date, address, cleaned_address, city, county, total_number_of_cases) %>% 
  group_by(cleaned_company, cleaned_address, city,county) %>% 
  filter(total_number_of_cases == max(total_number_of_cases)) 

sum(companytotals$total_number_of_cases)

write.csv(companytotals, "company_totals.csv")
```


```{r}
dates <- cleaned_master %>% 
  select(date, cleaned_company, number_active_cases) %>% 
  group_by(date) %>% 
  summarise(total = sum(number_active_cases)) %>% 
  arrange(desc(date))

dates
write.csv (dates,"active_cases_dates.csv")
```

#Group reports by Month
#Reports by Month https://public.flourish.studio/visualisation/5526542/ and https://public.flourish.studio/visualisation/5527511/ 
```{r}
month_counts <-cleaned_master %>%
  select(date,cleaned_city, cleaned_county, cleaned_company, industry, month) %>% 
  group_by(month) %>% 
  count() %>% 
  arrange(desc(n))
month_counts
#write.csv(month_counts,"month_counts.csv")

#Notes: June, 147, July, 142, Dec, 110 and Aug, 109 are the top months and only months above 100.
```

#City Analysis
#Top Ten Cities Chart https://public.flourish.studio/visualisation/5527182/ 
```{r}
cleaned_city_report <- cleaned_master %>% 
  select(date, city, cleaned_city) %>% 
  group_by(cleaned_city) %>% 
  count() %>% 
  arrange(desc(n)) 

cleaned_city_report

#write.csv(cleaned_city_report, "cleaned_city_report.csv")

#Report shows Springdale, 73; Jonesboro, 61; Rogers, 60

```

#County Analysis
#Top Ten Counties Chart https://public.flourish.studio/visualisation/5527376/ 
```{r}
#Analyze records by county location
cleaned_county_report <- cleaned_master %>% 
  select(date, city, county) %>% 
  group_by(county) %>% 
  count() %>% 
  arrange(desc(n))

cleaned_county_report

#write.csv(cleaned_county_report, "cleaned_county_report.csv")

#Notes: Benton, 95; Washington 83; Pope 68;Craighead 56 are the top counties.
#WELLS NOTE: Two of the wealthiest counties in Arkansas have the highest number of occupational reports
```

#Company Analysis
#Top 10 Companies Chart needs work: 
#Revised Look at the company names 
#add the function that produces percent of the whole - Hennigan can't figure out the funciton

```{r}
cleaned_company_report <- cleaned_master %>% 
  count(cleaned_company) %>% 
  arrange(desc(n)) 

cleaned_company_report
#write.csv(cleaned_company_report, "cleaned_company_report.csv")
  

Example: Here's a table filtering the dispositions column to show "no disposition" or "gone on arrival"
```{r}
Nothing <- SF %>% 
  filter(disposition == "ND" | disposition == "GOA")
```

- **Question**: Create a table with the serious actions including citations and arrests police took in the dispositions  

Arrest, Cited, Criminal Activation, SF Fire Dept Medical Staff engaged
```{r}
Busted <- SF %>% 
  filter(disposition == "ARR" | disposition == "CIT" | disposition == "CRM" | disposition == "SFD") %>% 
  count(disposition) %>% 
  arrange(desc(n))
```
- **EXERCISE** - A Basic chart of the crime data
```{r}
ggplot(Years, aes(x = year, y = n)) + 
  geom_bar(stat = "identity") +
  #coord_flip() +    #this makes it a horizontal bar chart instead of vertical
  labs(title = "Homeless Calls Per Year, San Francisco", 
       subtitle = "SF PD Service Call Data, 3/2016-11/2019",
       caption = "Graphic by Wells",
       y="Number of Calls",
       x="Year")
```

A chart using a dplyr filtering language
```{r}
Years %>% 
  filter(year >= 2017) %>% 
  ggplot(aes(x = year, y = n)) +
  geom_bar(stat = "identity") +
  #coord_flip() +    #this makes it a horizontal bar chart instead of vertical
  labs(title = "Homeless Calls After 2017, San Francisco", 
       subtitle = "SF PD Service Call Data, 2017-2019",
       caption = "Graphic by Wells",
       y="Number of Calls",
       x="Year")
```

A more complex filter
```{r}
SF %>% 
  filter(!is.na(common_location)) %>% 
  count(common_location) %>% 
  top_n(10, n) %>% 
  ggplot(aes(x = common_location, y = n)) +
  geom_bar(stat = "identity") +
  coord_flip() +    #this makes it a horizontal bar chart instead of vertical
  labs(title = "Popular Spots for Homeless, San Francisco", 
       subtitle = "SF PD Service Call Data, 2016-2019",
       caption = "Graphic by Wells",
       y="Number of Calls",
       x="Places")
```

- **Question**: Chart the total dispositions.  

Filter for at least 100 actions. Add color, export image to Blackboard.

```{r}
Action %>% 
  filter(n > 100) %>% 
  ggplot(aes(x = reorder(disposition, n), y = n, fill=n)) + 
  geom_bar(stat = "identity", show.legend = FALSE) +
  coord_flip() +    #this makes it a horizontal bar chart instead of vertical
  labs(title = "Action on Homeless Calls, San Francisco", 
       subtitle = "SF PD Service Call Data, 3/2016-11/2019",
       caption = "Graphic by Wells",
       y="Number of Calls",
       x="Action")
```

# Part 3: Cleaning Dispositions

Making our charts less ugly

The disposition column is in cop-speak. We need to clean it up

Step #1: Duplicate the column you want to mess with
```{r}
SF$disposition1 <- SF$disposition
```
Rename specific strings. Example:  

str_replace_all(test.vector, pattern=fixed('-'), replacement=fixed(':') )

Details on string manipulation:  

https://dereksonderegger.github.io/570L/13-string-manipulation.html

We can do this to replace ABA with "Abated"
```{r}
SF$disposition1 <- str_replace_all(SF$disposition1, pattern=fixed('ABA'), replacement=fixed('Abated') )
#Again with ADM
SF$disposition1 <- str_replace_all(SF$disposition1, pattern=fixed('ADM'), replacement=fixed('Admonished') )
```
We can do that 19 times. OR....  

Look at this example using a lookup table to replace all the values    
https://stackoverflow.com/questions/50615116/renaming-character-variables-in-a-column-in-data-frame-r   

Build a table to translate the Cop Speak to English:  
```{r}
dispo_lkup <- c(ABA="Abated", ADM="Admonish", ADV="Advised", ARR="Arrest", CAN="Cancel", CSA="CPSA", 
                CIT="Cited", CRM="Criminal", GOA="Gone", HAN="Handled", NCR="No_Criminal", ND="No_Dispo", 
                NOM="No_Merit", PAS="PlaceSecure", REP="Report", SFD="Medical", UTL="Unfound", VAS="Vehicle_Secure", '22'="Cancel")

#22="Cancel" was handled differently because it is a numeric value: '22'="Cancel"

#This scans "disposition", finds ABA and replaces with Abated, finds ARR, replaces with Arrest, etc
SF$disposition1 <- as.character(dispo_lkup[SF$disposition])
```

Rerun Action with disposition1
```{r}
Action <- SF %>% 
  count(disposition1) %>% 
  arrange(desc(n))
```
Compare our renamed variables to the original disposition
```{r}
Action <- SF %>% 
  count(disposition1, disposition) %>% 
  arrange(desc(n))
```
We have codes not listed on the sheet   

NA	Not recorded	4339

Get rid of the space
```{r}
SF$disposition <- gsub("Not recorded", "Not_Recorded", SF$disposition)
```

Add to the list
```{r}
dispo_lkup <- c(ABA="Abated", ADM="Admonish", ADV="Advised", ARR="Arrest", CAN="Cancel", CSA="CPSA", 
                CIT="Cited", CRM="Criminal", GOA="Gone", HAN="Handled", NCR="No_Criminal", ND="No_Dispo", 
                NOM="No_Merit", PAS="PlaceSecure", REP="Report", SFD="Medical", UTL="Unfound", 
                VAS="Vehicle_Secure", '22'="Cancel", Not_Recorded="NotRecorded")
```
Rerun  
```{r, echo=FALSE}
SF$disposition1 <- as.character(dispo_lkup[SF$disposition])
```
#
```{r}
Action <- SF %>% 
  count(disposition1) %>% 
  arrange(desc(n))
```
Chart Dispositions  
```{r}
Action %>% 
  filter(n > 100) %>% 
  ggplot(aes(x = reorder(disposition1, n), y = n, fill=n)) + 
  geom_bar(stat = "identity", show.legend = FALSE) +
  coord_flip() +    #this makes it a horizontal bar chart instead of vertical
  labs(title = "Action on Homeless Calls, San Francisco", 
       subtitle = "SF PD Service Call Data, 3/2016-11/2019",
       caption = "Graphic by Wells",
       y="Number of Calls",
       x="Action")
```
- **Parse out police codes from narrative: original_crime_type_name**
Look at the Types table: some columns have one code, some have two.
919	2879
915 Sleeper	290

Some are separated by a slash
915/919	161

We need to unpack that
- **Cleaning Sequence**
```{r}
#convert all text to lowercase
SF$crime1 <- tolower(SF$original_crime_type_name)
#Replace / with a space
SF$crime1 <- gsub("/", " ", SF$crime1)
#Replace '
SF$crime1 <- gsub("'", "", SF$crime1)
#fix space in homeless complaint
SF$crime1 <- gsub("homeless complaint", "homeless_complaint", SF$crime1)
#split data into two columns
SF <- separate(data = SF, col = crime1, into = c("crime2", "crime3", "crime4"), sep = " ", extra = "merge", fill = "right")
```
Look at the categories now
```{r}
Types2 <- SF %>% count(crime2) %>% 
  group_by(crime2) %>% 
  arrange(desc(n))
```
- **Question** Take the top 10 crime categories from Type2  
Relabel them from the numeric radio codes into English   
Using the technique earlier in "Build a table to translate the Cop Speak to English"   
Relabel the offenses 

```{r}
clean <- c(homeless_complaint="homeless_complaint", '915'="homeless_call", '919'="sit_lying", '920'="aggress_solicit", '915s'="homeless_call", '915x'="homeless_call", drugs="drugs", '601'="trespasser",
           poss="poss", aggressive="aggressive", '811'="intoxicated")
```

```{r}
SF$crime2 <- as.character(clean[SF$crime2])
```
Look at the categories now
```{r}
Types2 <- SF %>% count(crime2) %>% 
  group_by(crime2) %>% 
  arrange(desc(n))
```
- **Question:** Make a chart from your cleaned data  

Basic chart but with a messed up x axis
```{r}
Types2 %>% 
  ggplot(aes(x = crime2, y = n, fill=n)) + 
  geom_bar(stat = "identity") +
  coord_flip() +    #this makes it a horizontal bar chart instead of vertical
  labs(title = "Top 10 Homeless Complaints, San Francisco", 
       subtitle = "SF PD Service Call Data, 3/2016-11/2019",
       caption = "Graphic by Wells",
       y="Number of Calls",
       x="Complaint")
```
Chart with a fixed x axis scale; No values filtered out; Labels added to bars
```{r}
Types2 %>% 
  filter(!is.na(crime2)) %>% 
  #filter(crime2!=" ") %>%  - a crude alternative to previous line!
  ggplot(aes(x = reorder(crime2, n), y = n, fill=n)) + #reorder sorts the bars
  geom_bar(stat = "identity", show.legend = FALSE) +
  geom_text(aes(label = n), hjust = -.1, size = 3) +
  scale_y_continuous(limits=c(0, 175000)) + #fixes scientific notation
  coord_flip() +    #this makes it a horizontal bar chart instead of vertical
  labs(title = "Top 10 Homeless Complaints, San Francisco", 
       subtitle = "SF PD Service Call Data, 3/2016-11/2019",
       caption = "Graphic by Wells",
       y="Number of Calls",
       x="Complaint")
```

# Part 4: Using Mutate, Pct Calcs

mutate - Create new column(s) in the data, or change existing column(s). 

mutate() adds new variables and preserves existing

Example:
mtcars <- as.data.frame(mtcars)
View(mtcars)

mtcars2 <- mtcars %>% as_tibble() %>% mutate(
  cyl2 = cyl * 2,
  cyl4 = cyl2 * 2
)

Process dates using lubidate
```{r}
SF <- SF %>% 
  mutate(yearmo = format(call_date, "%Y-%m"))
```

Chart the number of calls by year and month
```{r}
SF %>% 
  count(yearmo) %>% 
  group_by(yearmo) %>% 
  ggplot(aes(x = yearmo, y = n, fill=n)) +
  geom_bar(stat = "identity") +
  theme(axis.text.x = element_text(angle=90)) +
  #Changes angle of x axis labels
  #coord_flip() +    #this makes it a horizontal bar chart instead of vertical
  labs(title = "Homeless Calls After 2017, San Francisco", 
       subtitle = "SF PD Service Call Data by Month 2017-2019",
       caption = "Graphic by Wells",
       y="Number of Calls",
       x="Year")
```

Percentage change per month
```{r}
PCT_CHG_CALLS <- SF %>% 
  select(original_crime_type_name, disposition, address, call_date2, yearmo) %>% 
  count(yearmo) %>% 
  mutate(difference = (n-lag(n))) %>% 
  mutate(pct_change = (difference/abs(lag(n)))*100)
```

- **Use grepl to search and tabulate**

grep and grepl: see ??grep  

http://www.endmemo.com/program/R/grepl.php  

Cleaning Sequence

```{r}
#convert all text to lowercase
SF$crime1 <- tolower(SF$original_crime_type_name)
```

- **Search for term, rename, put in new column called "cleaned"**
```{r}
x915 <- SF %>% 
  filter(grepl ("915", original_crime_type_name)) %>% 
  mutate(cleaned = "homeless_complaint")

x919 <- SF %>% 
  filter(grepl ("919", original_crime_type_name)) %>% 
  mutate(cleaned = "sitting_lying")

xsleep <- SF %>% 
  filter(grepl ("sleep", original_crime_type_name)) %>% 
  mutate(cleaned = "sleep")

xaggr <- SF %>% 
  filter(grepl ("aggr", original_crime_type_name)) %>% 
  mutate(cleaned = "aggressive")

xdrug <- SF %>% 
  filter(grepl ("drug", original_crime_type_name)) %>% 
  mutate(cleaned = "drug")

xhomeless <- SF %>% 
  filter(grepl ("homeless_complaint", crime2)) %>% 
  mutate(cleaned = "homeless_complaint")

#Moe, Brooke's Work: 
xnoise <- SF %>% 
  filter(grepl ("415", original_crime_type_name)) %>% 
  mutate(cleaned = "noise")

xposs <- SF %>% 
  filter(grepl ("poss", original_crime_type_name)) %>% 
  mutate(cleaned = "possession")

xtrespasser <- SF %>% 
  filter(grepl ("601", original_crime_type_name)) %>% 
  mutate(cleaned = "trespasser")

xsolicit <- SF %>% 
  filter(grepl ("920", original_crime_type_name)) %>% 
  mutate(cleaned = "solicit")

xinterview <- SF %>% 
  filter(grepl ("909", original_crime_type_name)) %>% 
  mutate(cleaned = "interview")

xtent <- SF %>%
  filter(grepl ("tent", crime1)) %>%
  mutate(cleaned="tent")

xdog <- SF %>%
  filter(grepl ("dog", crime1)) %>%
  mutate(cleaned="dog")

xchopshop <- SF %>%
  filter(grepl ("chop shop", crime1)) %>%
  mutate(cleaned="chopshop")

xpanhandling <- SF %>%
  filter(grepl ("panhandling", crime1)) %>%
  mutate(cleaned="panhandling")

xmusic <- SF %>%
  filter(grepl ("music", crime1)) %>%
  mutate(cleaned="music")
```
Create new dataframe using rbind 
```{r}
new_total <- rbind(xhomeless, x915, x919, xaggr, xdrug, xsleep, xnoise, xposs, xtrespasser, xsolicit, xinterview, xtent, xdog,
                   xchopshop, xpanhandling, xmusic)
```
Count it up!
```{r}
Total_Calls_Master <- new_total %>% 
  count(cleaned) %>% 
  arrange(desc(n))
#rename columns
colnames(Total_Calls_Master)[1:2] <- c("Complaints", "Number")
#export
write_csv(Total_Calls_Master, "Total_Calls_Master.csv")
```
Make into html table
```{r}
#install.packages("kableExtra")
library(kableExtra)
```

```{r}
#This makes html tables called "kables"
Total_Calls_Master %>% 
  kable() %>%
  kable_styling("striped")
```
Export from Viewer as .png

- **Task: Tabulate complaints by day of the week**  

https://github.com/profrobwells/Data-Analysis-Class-Jour-405v-5003/blob/master/Readings/dealing-with-dates.pdf

```{r}
SF <- SF %>% 
  mutate(weekday = wday(call_date, label=TRUE, abbr=FALSE))
```
Build a summary table with the days of the week with the greatest
number of calls. Create a graphic. Then build a table to see if the complaints vary by day

Below from Matthew Moore, Katy Seiter, Wells edited
```{r}
SF <- SF %>% 
  mutate(weekday = wday(call_date, label=TRUE, abbr=FALSE))

Weekday_Count <- SF %>%
  select(weekday, crime_id) %>%
  count(weekday) %>%
  arrange(desc(n))
```
Graphic of calls by weekdays

```{r}
Weekday_Count %>% 
  ggplot(aes(x = weekday, y = n, fill=n)) +
  geom_bar(stat = "identity", show.legend = FALSE) +
  theme(axis.text.x = element_text(angle=90)) +
  #Changes angle of x axis labels
  #coord_flip() +    #this makes it a horizontal bar chart instead of vertical
  labs(title = "Homeless Calls By Weekday in San Francisco", 
       subtitle = "SF PD Service Call Data 2017-2019",
       caption = "Graphic by Moore and Seiter",
       y="Number of Calls",
       x="Weekday")
```

Create a Bubble graphic
```{r}
ggplot(data = Weekday_Count) + 
  geom_point(mapping = aes(x = weekday, y = n, size = n, color = n), show.legend = FALSE) +
  theme(axis.text.x = element_text(angle=90)) +
  labs(title = "Homeless By Weekday in San Francisco", 
       subtitle = "SF PD Service Call Data 2017-2019: Source: SFPD",
       caption = "Graphic by Moore and Seiter",
       y="Number of Calls",
       x="Weekday")
```

Improved bubble chart

```{r}
ggplot(Weekday_Count, aes(x = weekday, y = n)) +
  xlab("Weekday") +
  ylab("Number of Calls") +
  theme_minimal(base_size = 12, base_family = "Georgia") +
  geom_point(aes(size = n, color = n), alpha = 0.7, show.legend = FALSE) +
  scale_size_area(guide = FALSE, max_size = 15) +
  labs(title = "Homeless By Weekday in San Francisco", 
       subtitle = "SF PD Service Call Data 2017-2019: Source: SFPD",
       caption = "Graphic by Moore and Seiter")
```
- **Task #3: Calls vs Dispositions**

What calls resulted in arrests? What calls resulted in citations?
```{r}
Action2 <- SF %>%
  select(crime_id, original_crime_type_name, disposition) 
```
We need to pair the crime type and disposition and then count them

From Michael Adkison:
```{r}
callsarrest <- Action2 %>% 
  filter(grepl("ARR", disposition)) %>% 
  mutate(cleaned = "Arrest")
```

To quickly format into percents, load formattable
```{r}
#install.packages("formattable")
library(formattable)

callsarrest2 <- callsarrest %>% 
  arrange(original_crime_type_name, disposition) %>% 
  count(original_crime_type_name) %>% 
#mutate(PctTotal = (n/441)) %>% 
  arrange(desc(n))

colnames(callsarrest2)[1:2] <- c("Complaints", "Arrests") 
```
Build a table to translate the Cop Speak to English:

```{r}
clean <- c('Homeless Complaint'="homeless_complaint", homeless_complaint="homeless_complaint", '915'="homeless_complaint", 
           '919'="Sit_lying", '920'="Aggress_solicit", '915s'="homeless_complaint", '915x'="homeless_complaint", 
           drugs="drugs", '601'="trespasser", poss="poss", aggressive="aggressive", '811'="intoxicated", 
           'Drugs / 915'="Drugs", 'Drugs/915'="Drugs")
```
This scans "disposition", finds ABA and replaces with Abated, finds ARR, replaces with Arrest, etc
callsarrest2$Complaints <- as.character(clean[callsarrest2$Complaints])

```{r}
callsarrest3 <- callsarrest2 %>% 
  select(Complaints, Arrests) %>% 
  group_by(Complaints) %>% 
  summarise(total = sum(Arrests)) %>% 
  mutate(PctTotal = (total/441)) %>% 
  arrange(desc(total))

colnames(callsarrest3)[2] <- "Arrests" 
callsarrest3$PctTotal <- percent(callsarrest3$PctTotal)

#This makes kables
callsarrest3 %>% 
  kable() %>%
  kable_styling("striped")
```
# Part 5: Trends over time

- **Question**: What were the common days for arrests?
```{r}
SF %>%
  select(weekday, crime_id, disposition) %>%
  filter(grepl("ARR", disposition)) %>%
  count(weekday) 
```

Make bubble chart
```{r}
SF %>%
  select(weekday, crime_id, disposition) %>%
  filter(grepl("ARR", disposition)) %>%
  count(weekday) %>% 
  ggplot(aes(x = weekday, y = n)) +
  xlab("Weekday") +
  ylab("Arrests") +
  theme_minimal(base_size = 12, base_family = "Georgia") +
  geom_point(aes(size = n, color = n), alpha = 0.7, show.legend = FALSE) +
  scale_size_area(guide = FALSE, max_size = 15) +
  labs(title = "Homeless Arrests By Weekday in San Francisco", 
       subtitle = "SF PD Service Call Data 2017-2019: Source: SFPD",
       caption = "Graphic by Wells") 
```

- **Question**: What is the trend for arrests over the time period?  

```{r}
SF %>% 
  filter(grepl("ARR", disposition)) %>%
  count(yearmo) %>% 
  group_by(yearmo) %>% 
  ggplot(aes(x = yearmo, y = n, fill=n)) +
  geom_bar(stat = "identity", show.legend = FALSE) +
  geom_smooth(method = lm, se=FALSE, color = "red") +
  theme(axis.text.x = element_text(angle=90)) +
  #Changes angle of x axis labels
  #coord_flip() +    #this makes it a horizontal bar chart instead of vertical
  labs(title = "Arrest Trends on Homeless Calls in San Francisco", 
       subtitle = "Arrests Based on SF PD Service Call Data by Month 2017-2019",
       caption = "Graphic by Wells",
       y="Number of Calls",
       x="Year")
```

- **Question**: What are the hours most likely for complaints?    
```{r}
#format to hours
SF$hour <- hour(SF$call_date_time)

SF %>% 
  count(hour) %>% 
  group_by(hour) %>% 
  ggplot(aes(x = hour, y = n, fill=n)) +
  geom_bar(stat = "identity", show.legend = FALSE) +
  theme(axis.text.x = element_text(angle=90)) +
  #Changes angle of x axis labels
  #coord_flip() +    #this makes it a horizontal bar chart instead of vertical
  labs(title = "Hours of Homeless Calls, San Francisco", 
       subtitle = "SF PD Service Call Data by Month 2017-2019",
       caption = "Graphic by Wells",
       y="Number of Calls",
       x="Hour")  
```
- **Question**: Examine some of the charting options on this tutorial and adapt them to this data using any chart you want
# https://paldhous.github.io/wcsj/2017/


# --30-- 

