---
title: "PPP Data"
author: "Abby Zimmardi and Rob Wells"
date: "1/27/2021"
output: html_document
---

```{r}
library(tidyverse)
#install.packages("rio")
#install.packages(dplyr)
library(dplyr)
```

```{r}
PPP <- rio::import('/Users/abbyzimmardi/Downloads/Data Spring 2021/OSHA/150k plus 0808/PPP Data 150k plus 080820.csv')

#WELLS IMPORT:
# PPP <- rio::import('/Users/rswells/Dropbox/Classes/Data Fall 2020/ArkansasCovid/PPP Loan Data 150k plus 0808/PPP Data 150k plus 080820.csv')
```


```{r}
PPP2 <- PPP %>% 
  filter(State == "AR")
#PPP2
```
#Clean Names, Make everything in BusinessName have an underscore in between
```{r}
PPP2$BusinessName  <- gsub("[[:punct:]]", "", PPP2$BusinessName)
PPP2$BusinessName  <- str_trim(PPP2$BusinessName, side =c("both"))
PPP2$BusinessName <- str_replace_all(PPP2$BusinessName, pattern=fixed(' '), replacement=fixed('_') )
PPP2
```




```{r}
# OSHA <- rio::import('/Users/abbyzimmardi/Downloads/Data Spring 2021/OSHA/AR Closed Complaints Jan. 13.xlsx')
# OSHA

#WELLS IMPORT
OSHA <- rio::import('https://github.com/profrobwells/Spring2021Data/blob/main/closed_complaints_jan_13.xlsx?raw=true', which="AR")
```

#Rename columns
```{r}
OSHA <- OSHA %>%
  rename(State = 'Site State', Address = 'Site Address 1', Zip = 'Site Zip', City = 'Site City', BusinessName = 'Estab Name')
OSHA
```
#WELLS EDIT
#clean
#Make everything have an underscore in between
```{r}
OSHA$BusinessName<- gsub("[[:punct:]]", "", OSHA$BusinessName)
OSHA$BusinessName <- str_trim(OSHA$BusinessName, side =c("both"))
#This is the power cleaner command!!!
OSHA$BusinessName<- str_replace_all(OSHA$BusinessName, pattern=fixed(' '), replacement=fixed('_') )
OSHA$BusinessName = toupper(OSHA$BusinessName)
OSHA

```


#JOIN BY NAME 
#Seven Matches!!!
```{r}
OSHA_PPP <- inner_join(PPP2, OSHA, by=c("BusinessName"="BusinessName"))
```



#Additional Strategies
--duplicate business names into a new column and do a radical cleaning for both
OSHA$BizName2 <- OSHA$BusinessName
PPP$BizName2 ....

--use this to get rid of LLC and INC in both business names.

OSHA$BizName2<- str_replace_all(OSHA$BizName2, pattern=fixed('_INC'), replacement=fixed('') )


