---
title: "PPP Data"
author: "Abby Zimmardi"
date: "1/20/2021"
output: html_document
---

```{r}
library(tidyverse)
#install.packages("rio") 
```
#WELLS COMMENT: The next level in R is to make sure your data can be downloaded by anyone. This file is on your hard drive and I can't get to it. Better to put the file on your GitHub and download it from there so everyone can access the script and data. The problem is this is such a large file (130 mb) that it exceeds the GitHub storage of 25 mb. I'll ask Sean how to deal with this.
```{r}
PPP <- rio::import('/Users/abbyzimmardi/Downloads/Data Spring 2021/OSHA/150k plus 0808/PPP Data 150k plus 080820.csv')
```

#WELLS EDIT:
```{r}
PPP <- rio::import('/Users/rswells/Dropbox/Classes/Data Fall 2020/ArkansasCovid/PPP Loan Data 150k plus 0808/PPP Data 150k plus 080820.csv')
```




```{r}
PPP2 <- PPP %>% 
  filter(State == "AR")
PPP2
```
```{r}
OSHA <- rio::import('/Users/abbyzimmardi/Downloads/Data Spring 2021/OSHA/AR Closed Complaints Jan. 13.xlsx')
```



#WELLS EDIT:
```{r}
OSHA <- rio::import('https://github.com/profrobwells/Spring2021Data/blob/main/closed_complaints_jan_13.xlsx?raw=true', which="AR")
```




```{r}
OSHA <- OSHA %>%
  rename(State = 'Site State', Address = 'Site Address 1', Zip = 'Site Zip', City = 'Site City')
OSHA
```
```{r}
#install.packages(dplyr)
library(dplyr)
```
#Join the tables
newtable <- inner_join(table1, table2, by=c("fieldname"="fieldname"))
```{r}
OSHA_PPP <- inner_join(PPP2, OSHA, by=c('Address"="Address"))
```

#WELLS EDIT
#WELLS EDIT
```{r}
head(PPP2$BusinessName)
```

```{r}
OSHA <- OSHA %>%
  rename(BusinessName = `Estab Name`)
head(OSHA)
```

#JOIN BY NAME 
```{r}
OSHA_PPP <- inner_join(PPP2, OSHA, by=c("BusinessName"="BusinessName"))
```


#You will need to clean either the business names or the addresses to make them match.
#See this tutorial and we can discuss.
https://profrobwells.github.io/HomelessSP2020/SF_311_Calls_UofA.html#part_3:_cleaning_dispositions









